---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# filetools

The purpose of this package is to provide some functionality that can be handy
when you have a number of data files and you want to check for the
existence of certain variables (names) within these files.

In a perfect world with perfect data documentation this would no be needed but
in practice people do not always know which (of the many versions) of their
files that contains certain variables.

### Installation

To install from GitHub use:

```{r, eval = F}
devtools::install_github("thebackman/filetools")
```

### Usage

To find variables within a file use the `find_vars_in_files` function. The
syntax is easy. There are only five arguments:

1. absolute path to folder with sav / csv-files
2. include subfolders, TRUE / FALSE
3. what kind of files do we have (SPSS = sav, csv = csv)
4. what string to search for
5. print HTML-report

```{r, eval = FALSE}
# to test it with the installed example data files, use
find_vars_in_files(
  path = system.file("extdata", package="filetools"),
  subf = F,
  file_type = "sav",
  searchstring = "id",
  HTML_out = F)

find_vars_in_files(
  path = system.file("extdata", package="filetools"),
  subf = F,
  file_type = "sav",
  searchstring = "fruit",
  HTML_out = F)
```

### Details

The HTML-file is called *files.html*. The search string is just a regular
expression that allows arbitray characters before and after the provided string.

### Future

In the future I might add some matching possibility, searching of labels,
optional variable removal etcetera. 

### Notes

I hope you find what you are looking for :-)
